Identity Blockchain - Proof of Identity

### 2022-07-23 paper.tex
registerKid using verifyProof

\newpage
\section{Registering identity key ($\khk$)}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidUsed;
	mapping(uint => uint) public ninKidKpUsed;
  mapping(uint => bool) public kidInvalid;

  function register(
    uint hNin, // hNin = H(Nin)
		uint hNinKid,
		uint hNinKidKp,
		bool invalidate, //true if someone stole your previous id
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC,
  ) public {
		//Setting public arguments
		uint[] memory inputValues = new uint[](3);
		inputValues[0]=hNin;
		inputValues[1]=hNinKid;
		inputValues[2]=hNinKidKp;

    require(verifyProof(
			proofPointA,
			proofPointsB,
			proofPointC,
			inputValues
		));

    uint previousHNinKid = ninKidUsed[hNin];
    if (previousHNinKid != hNinKid and invalidate == true) {
			//If they are different, we need to invalidate old Kid
			kidInvalid[previousHNinKid] = true;
		}
		require(!kidInvalid[hNinKid]);

		ninKidUsed[hNin] = hNinKid;

		ninKidKpUsed[hNinKid] = hNinKidKp;

  }

\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

@@

\newpage
\underline{Pseudo-circom code}
Statements we need to check:
\begin{itemize}
	\item Check first step (Register $\kid$) still valid

\end{itemize}

>>>>

\newpage
\section{Registering $\kid$}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidUsed;
  mapping(uint => bool) public kidInvalid;

  function registerKid(
    uint hNin, // hNin = H(Nin)
    uint vKid, // vKid = KidPrivate("registerKid")
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointB,
		uint[2] memory proofPointC,
		bool invalidate
  ) public {
		//Setting public arguments
		uint[] memory inputValues = new uint[](2)
		inputValues[0] = hNin;
		inputValues[1] = vKid;

		require(
			verifyProof(
				proofPointA,
				proofPointB,
				proofPointC,
				inputValues
			)
		);

    uint previousKey = ninKidUsed[hNin];
    if (previousKey == vKid) return; // already registered

 		uint previousVKid = ninKidUsed[hNin];
    if (previousVKid != vKid and invalidate == true) {
			//If they are different, we need to invalidate old Kid
			kidInvalid[previousVKid] = true;
		}
		require(!kidInvalid[vKid]);

    ninKidUsed[hNin] = vKid;
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

@@

\newpage
\underline{Pseudo-circom code}
Statements we need to check:
\begin{itemize}
	\item CA
\end{itemize}
